Think deep for reef resilience

### 2025-07-11 paper/paper_draft.qmd
Indicate why the range is used
Avoid false precision!

Given the uncertainties present, the proportion of reefs that display capacity to maintain
coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of 10 to
20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
[-@perry2015] and Desbians et al., [-@desbiens] providing indications of the lower and upper
bounds respectively.

>>>>

Given the uncertainties present, the proportion of reefs that display capacity to maintain
coral cover above a given $\beta_{0}$ threshold is examined. An indicative range of 10 to
20% is used (inclusive, with a step size of 1%). The range was informed by Perry et al.,
[-@perry2015] and Desbians et al., [-@desbiens] providing plausible indications of the
lower and upper bounds respectively. Robustness of the conclusions drawn to the uncertainty
in the precise value of $\beta_{0}$ for all reefs can then be assessed by using a range.
